---
name: Catalina
surname: Cañizares-Escobar
position: "PhD Candidate"
address: "Florida International University"
phone: +1 00000000
email: "ccani007@fiu.edu"
twitter: CatalinaCaniza1
github: ccani007
orcid: 0000-0002-6854-5205
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
docname: CV
output: vitae::awesomecv
editor_options: 
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(tidyverse)
library(here)
library(readr)
library(scholar)
```



# Education

```{r education}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD in Social Welfare", "2020-", "Florida International University", "Miami, United States",
  "Master in Clinical and Health Psychology", "2014", "Universidad de los Andes", "Bogotá, Colombia",
  "Pyschology", "2012", "Universidad de los Andes", "Bogotá, Colombia"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```



# Professional Experience

```{r professional_experience_tribble, include=FALSE}
professional_experience <- tribble(
  ~title, ~unit, ~startMonth, ~startYear, ~endMonth, ~endYear, ~where, ~detail,
  "Academic Coordinator", "School of Education", "October", 2017, "July", 2020, "Universidad de los Andes", 
  "Arrangement of academic matters like schedules, lectures, classes and summer school for undergraduate, postgraduate and PhD programs of the School of Education. 
  \\begin{itemize}
        \\item Assess the quality of academic processes.
        \\item Support students throughout their programs and warrant their graduation.
        \\item Systematize information and use it to improve academic processes.
    \\end{itemize}",
  "Clinical Psychologist", "Office of student affairs", "March", 2017, "October", 2017, "Universidad de los Andes", 
  "Provided psychological attention for undergraduate and graduate students. \\begin{itemize}
        \\item Designed psycho-educational workshops for students.
        \\item Mediated in disciplinary cases.
        \\item Supported the development of the protocol to report cases of sexual abuse and harassment (MAAD).
    \\end{itemize}",
  "Clinical manager of the Center of Psychology, Casa-Espinosa", "Department of Psychology", "February", 2014, "March", 2017, "Universidad de los Andes", 
  "Supervised students practicum of the Master in Clinical and Health Psychology. 
  \\begin{itemize}
        \\item Guided the development of intervention guidelines for the center of psychological attention.
        \\item Implemented technological features to gather information from patients to be used in further investigation.  
        \\item Represented the center at the Colombian Network of Psychological University Centers Red ISUAP 
    \\end{itemize}",
  "Clinical Practicum", "Center for Children and Families", "June", 2013, "August", 2013, "Florida International University", 
  "Implemented the STP Protocol for children with ADHD and related behavioral and emotional challenges.",
  "Clinical Practicum", "Casa Espinosa", "August", 2012, "May", 2013, "Universidad de los Andes", 
  "Provided psychological attention (evaluation and intervention) to outpatients.",
  "Clinical Practicum", "Oncology Unit: Ardila Lule", "January", 2011, "December", 2011, "Fundación Santa Fe de Bogotá", "Performed psychological evaluation for oncologic patients"
  )

```

```{r professional_experience}
professional_experience %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""),
    where = where, .protect = F
  )
```

# Research

```{r research_tribble,include=FALSE}
research <- tribble(
  ~title, ~unit, ~startYear, ~endMonth, ~endYear, ~where, ~ professor, ~detail,
  "Research Assistant", "School of Social Work", 2022, "Present", NA, "Boston College", "Maria Piñeros-Leaño, Ph.D.", "Mothers and Children of All Nations Defying the Odds.  \\begin{itemize}
     \\item Analysis of qualitative data. 
  \\end{itemize}",  
  "Research Assistant", "Department of psychology", 2012, "Present", NA, "Universidad de los Andes", "Yvonne Gómez, Ph.D.", "Depression and genetics.  
  \\begin{itemize}
     \\item Review and select literature, collect and analyze data, evaluate and write proposals for publication. 
  \\end{itemize}",
  
  "Research Assistant", "Department of psychology", 2018, "January", 2019, "Universidad de los Andes", "Leonidas Castro Ph.D.",
  "Adaptation and Validation of the Unified Protocol for victims of armed conflict in Colombia.
  \\begin{itemize}
     \\item Implement the Unified Protocol with victims of armed conflict in Colombia
   \\end{itemize}")
```

```{r research}

research %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startYear} - {endMonth} {endYear}",.na = ""),
    where = where, .protect = F)

```


# Teaching Experience 

```{r teaching_tribble, include=FALSE }
teaching <-  tribble(
  ~title, ~unit, ~startMonth, ~startYear, ~endMonth, ~endYear, ~where, ~detail,
  "Teacher Assistant", "Bistatistics",  "June", 2022, "August", 2022, "Florida International University", "Assisted the Avanced R class for posgraduate students", 
  "Graduate Teaching Assistantship", "Spanish Center", "January", 2013, "December", 2013, "Universidad de los Andes", 
  "Tutored undergraduate students in Spanish writing skills. 
  \\begin{itemize}
        \\item Developed and implemented activities and rubrics to evaluate skills in Spanish writing.
        \\item Assisted the course Fundamentals of Psychology (spring, 2013 and fall, 2013).
    \\end{itemize}",
  
  "Undergraduate Teaching Assistantship", "Department of Psychology", "January", 2010, "May", 2010, "Universidad de los Andes", 
  "Assisted the course Neuroscience 1 (Spring, 2010)")

```

```{r teaching}
teaching %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""),
    where = where, .protect = F)
```

# Publications

Gómez‑Maquet, Y., Velásquez, M. M., **Cañizares C**., Uribe, C., Manzanilla, I., Ferro, E., Agudelo, D. M., Arenas, Á., & Lattig, M. C. (2022). The role of cognitive schemas and childhood adversity in the likelihood of developing Major Depressive Disorder. Revista Latinoamericana de Psicología, 54. https://doi.org/10.14349/rlp.2022.v54.8

Gómez‑Maquet, Y, Angel J, **Cañizares C**, Lattig M, Agudelo D, Arenas A, Ferro E. (2019) The role of stressful life events appraisal in major depressive disorder.  Revista Colombiana de Psiquiatría (ISSN 0034-7450) In Press (-), pp. In Press. https://www.sciencedirect.com/science/article/pii/S003474501830088X

Galeano L, Gaviria A, **Cañizares C**, Uribe C, Ferro E, Arenas A, Gómez‑Maquet, Y., Lattig C. (2019) Assessment of Perception of Stressful life events as important factor in Major Depressive Disorder. European Neuropsychofarmacology. Volume 29, Supplement 3, pp S841-S842 https://www.sciencedirect.com/science/article/pii/S0924977X17305722

Lattig M, Villamizar V, Gaviria A, Angel J, **Cañizares C**, Ferro E, Arenas A, Gómez‑Maquet, Y. (2017) BDNF Methylation and Stress Response in a Clinical Population with Major Depressive Disorder.  Official Journal of the Society of Biological Psychiatry (ISSN 0006-3223). https://www.biologicalpsychiatryjournal.com/article/S0006-3223(17)30367-0/pdf

Horn A, **Cañizares C**, Gómez‑Maquet, Y.  (2014) Prevention of Adolescent Depression in the Spanish-Speaking. World. International Journal Of Environmental Research And Public Health (ISSN 1660-4601) 11 (6), pp. 5665-5683. https://www.mdpi.com/1660-4601/11/6/5665

# Software development 
Cañizares C, Macgowan M, Odom G (2022). tidyDisasters: A relational database of FEMA, EMDAT, and GTD disaster data sets. R package version 0.1.1, https://ccani007.github.io/tidyDisasters/.


Cañizares, C., Macgowan, M., Odom, G (2022). tidyYRBS. https://github.com/ccani007/tidyYRBS.git

# Conference presentations

**Cañizares C** (2023) Contributing to Scientific Reproducibility: Using R Markdown and Knitr to create reproducible research documents. *Presented at* the Society for Social Work and Research 27th Annual Conference - Battling Inequities and Building Solutions, Phoenix, AZ. 

**Cañizares C**, Macgowan M.J, Odom G. (2023) Risk Factors Associated with Suicide Attempts in U.S High School Students Since 2005: A Replication Study *Presented at* at the Society for Social Work and Research 27th Annual Conference - Battling Inequities and Building Solutions, Phoenix, AZ. 

Bursac Z, Rodriguez A, Williams R, Bhoite P, Gonzalez I, **Cañizares C**, Odom G. (2022) R for Data Science in Public Health. *Presented at* the International Data Science Conference Europe,  Belgrade, Serbia.

**Cañizares C**, Macgowan M.J, Odom G. (2022) It Just Takes a Question: The Development of tidyDisasters and tidyYRBS. *Invited Speaker* at the Data Science Conference US Health, Miami, FL. 

**Cañizares C**, Macgowan M.J. (2022) Interventions for Adolescent Suicidality in Latin America: A Systematic Review. *Poster* at the Society for Social Work and Research 26th Annual Conference - Social Work Science for Racial, Social, and Political Justice, Washington D.C. United States of America

**Cañizares C**, Gómez-Maquet Y, Velásquez M.M,  Lattig2 M.C, Uribe C, Manzanilla I, Ferro E, Agudelo DM, Arenas A. (2022). Childhood Adversity, Attributional Style, and Cognitive Schemas As Predictors of the Spanish Version of the State-Trait Depression Questionnaire Score. *Poster* at the Society for Social Work and Research 26th Annual Conference - Social Work Science for Racial, Social, and Political Justice, Washington D.C. United States of America

Gómez Y, Nicolás S, Spinel J, **Cañizares C**, Ángel J, Agudelo D, Lattig M, Arenas A, Ferro E. (2017) Diátesis cognitiva: Esquemas Maladaptativos Tempranos (EMT) en el Trastorno Depresivo Mayor (TDM). Presented at the VIII National Psychology Congress in Santiago de Chile, Chile. 

**Cañizares C**, García N. (2017) Utilización de pruebas psicométricas en psicología clínica y su relación con el entrenamiento en formulación transdiagnóstica en un programa de maestría clínica y de la salud. Presented at Congreso Colombiano de Psicología: Psicología y Construcción de Paz, Medellín, Colombia.

**Cañizares C**, Martinéz M, Estupiñan N, Gutiérrez, C.(2015) Desarrollo de Guías Clínicas en la Casa Espinosa-Centro de prácticas de Psicología Clínica, Universidad de los Andes. Panelist at the IV Forum of Clinical and Health Intervention Guidelines, Bogotá, Colombia.  

# Honors

```{r honors_tribble, include=FALSE }
honors <-  tribble(
  ~area, ~accomplishment, ~year, ~detail, ~where,
  "Fulbright", "Scholarship Fulbright-Minciencias", 2020, "Scholarship to conduct Doctoral studies in the United States of America","Bogotá",
  "Spanish Center Award", "Scholarship for posgraduate studies", 2013, "Awarded for academic excellence and proficient knowledge in Spanish writing skills", "Universidad de los Andes" ) 

```

```{r honors}
honors %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```


